Haploid Selection, Sex Ratio Bias, and Transitions Between Sex-Determination Systems

### 2017-09-28 LaTeX/Turnover.tex
added big sup ploid antag plot

@@

@@

\textcolor{red}{
Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection. For each type of haploid selection (gametic competition/ meiotic drive in males/females), give a regionplot where $h^\male=h^\female$, e.g., $h^\male=h^\female=0.75$ (or perhaps the value of $h$ we use in the regionplots we have, in which $w_{aa}=0.85$, $w_{Aa}=1$, $w_{AA}=1.05$). 
Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}). In Matts plot the axes were $s^\Hermaphrodite$ and $\alpha_{\Delta}^\Hermaphrodite$. 
Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }

\textcolor{red}{
We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures. Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection. 
Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}

>>>>

%to rotate figures
\usepackage{rotating}
\usepackage{pdflscape}

@@

\begin{landscape}
\begin{figure}[!h]
\centering
\centerline{
\includegraphics[width=\linewidth]{All_plot_combined_PloidAntag_Matt}
}
\caption{
A-D show when each of the neo-W haplotypes invade an internally stable equilibrium with $a$ fixed on the Y (found by setting $r=0$).
The y-axis shows directional selection in diploids of both sexes, $s^\female=s^\male$, and the x-axes show sex-specific drive, $\alpha_\Delta^\Hermaphrodite$, or haploid competition, $t^\Hermaphrodite$.
The top left and bottom right quadrants therefore imply ploidally-antagonistic selection (and these are the only places where.
Dominance is equal in both sexes, $h^\female=s^\male=3/4$. 
E-F show the temporal dynamics of neo-W frequency with parameters given by the asterisks in the corresponding A-D plot, with $r=1/200$, for four different $R$.
Black $R=1/1000$, Red $R=2/100$, Blue $R=1/10$, Green $R=1/2$.  
Dashed line in E-H gives ``fixation" of neo-W.
\textcolor{blue}{here and elsewhere, we may want to switch to plotting freq of neo-W in females, so that we can see if the difference from 0.5 is due to biased sex ratios or polymorphic SD}
}
\label{fig:regionPloidAntag}
\end{figure}
\end{landscape}

@@

\textcolor{red}{
Perhaps it would also be useful to add an 8 panel figure that features ploidally antagonistic selection. For each type of haploid selection (gametic competition/ meiotic drive in males/females), give a regionplot where $h^\male=h^\female$, e.g., $h^\male=h^\female=0.75$ (or perhaps the value of $h$ we use in the regionplots we have, in which $w_{aa}=0.85$, $w_{Aa}=1$, $w_{AA}=1.05$). 
Matt made a figure like this before but both Y$a$ and Y$A$ equilibria were plotted and there was no outline showing where the Y$a$ equilibrium is stable (as in Figure \ref{fig:regionplots}). In Matts plot the axes were $s^\Hermaphrodite$ and $\alpha_{\Delta}^\Hermaphrodite$. 
Add an asterisk to each region plot and show invasion in another panel, using those parameters and various $R$ (e.g., in the stye of \ref{fig:temporalOverdominance}). 
In an email, Sally has an example of ploidally-antagonistic selection where the neo-W fixes and $R=1/2$. This would cover that case and more. }
\textcolor{blue}{
made an attempt (Figure \ref{fig:regionPloidAntag})
}

\textcolor{red}{
We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures. Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection. 
Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}
\textcolor{blue}{
these figures are now done (\ref{fig:regionMaleDrive}-\ref{fig:regionFemaleGS}) (ensuring frequencies between 0 and 1), but yet to discuss in text.}
